Generating exact lattices in a WFST framework

### 2011-09-27 misc/papers/icassp12_lat/paper.tex
Adding new results in paper.tex at bottom
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@528 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

running on blades, using 64bit version with double float and lattice-simple-decoder

@@

experiment: changing lattice beam:

decoding beam:     15.0         15.0       15.0       15.0       15.0         15.0        15.0        15.0        15.0         15.0        15.0
lattice beam:      10.0          9.0        8.0        7.0        6.0          5.0         4.0         3.0         2.0          1.0         0.0
avg. link density: 23.56        16.0       10.82       7.26       4.91         3.38        2.38        1.77        1.4          1.17        1.0
realtime factor:    3.61         3.17       2.59       2.41       2.34         2.98 ?      3.21 ?      1.89        3.12 ?       1.78        --

@@

>>>>

running on blades, using 64bit version with double float and lattice-simple-decoder
realtime factor running on pcburget, 22989 frames (decode3.sh)

@@

1) experiment: changing lattice beam:
(lattices 443c040w and 444c040i have been reduced from 10.0 to 8.1 because of determinization memory problems)

decoding beam:     15.0         15.0       15.0       15.0       15.0         15.0        15.0        15.0        15.0         15.0        15.0
lattice beam:      10.0          9.0        8.0        7.0        6.0          5.0         4.0         3.0         2.0          1.0         0.0
avg. link density: 23.56        16.0       10.82       7.26       4.91         3.38        2.38        1.77        1.4          1.17        1.0
realtime factor:    2.317        2.114      2.006      1.941     1.900         1.855       1.835       1.797       1.769        1.737       ---

@@

2) experiment: changing decoding beam:

decoding beam:     16.0        15.0          14.0          13.0         12.0         11.0         10.0          9.0 (1 utt partial) 8.0 (2 partial)
lattice beam:       7.0         7.0           7.0           7.0          7.0          7.0          7.0          7.0                7.0
avg. link density:  7.4         7.26          7.04          6.74         6.33         5.71         4.9          4.08               3.09
realtime factor:    2.646       1.941         1.428         1.052        0.775        0.555        0.388        0.267              0.177
decoding WER:      11.51%       11.51%       11.54%        11.58%       11.75%       11.93%       12.32%        13.47%             15.41%
ins/del/sub:       118/57/474   118/57/474   118/57/476    119/56/478   124/57/482   131/58/484   140/58/497    164/56/540         197/61/611
utterances wrong:  227          227          227           227          228          228          229           236                246

oracle WER:        3.03%        3.08%        3.24%         3.37%        3.56%        4.02%        4.72%         6.45%              9.18%
ins/del/sub:       30/1/140     31/1/142     35/2/146      38/2/150     42/3/156     54/6/167     55/7/204      73/13/278          118/22/378
oracle utt wrong:  100          101          105           108          112          119          128           153                184

rescoring WER(15): 9.59%        9.59%        9.73%         9.80%        10.05%       10.26%       10.55%        11.82% (1 failed)  13.79% (2 failed)
ins/del/sub:       116/36/389   117/36/388   115/37/397    117/38/398   123/39/405   132/39/408   141/37/417    ---                ---
rescore utt wrong: 205          205          206           206          207          209          208           220                235

3) bigram vs. trigram decoding:

decoding lm:       bigram       trigram,pruned  bigram        trigram,pruned   bigram (just to see whether wider beams still help)
decoding beam:     15.0         15.0            13.0          13.0             16.0 
lattice beam:       9.0          9.0             9.2           9.2             10.0 (already quite big for lattice-oracle - more than 6GB RAM used)
avg. link density: 16.0         14.98           14.86         13.58            24.84
rt factor(old):     3.17         3.26            1.75         1.77              4.54

decoding WER:      11.51%       10.57%          11.58%        10.80%           11.51%
ins/del/sub:       118/57/474   116/44/436      119/56/478    120/47/442       118/57/474
utterances wrong:  227          214             227           215              227

oracle WER:        2.78%        2.84%           3.05%         3.19%            2.61%
ins/del/sub:       25/0/132     30/0/130        30/2/140      33/1/146         21/0/126
oracle utt wrong:  96           96              103           107              92

rescoring WER(15):  9.59%       9.64%           9.80%         9.87%            9.59%
ins/del/sub:       117/36/388   115/34/395      117/38/398    119/38/400       116/36/389
rescore utt wrong: 205          205             206           209              205

4) lattice vs. n-best lists
decoding with trigram, pruned

decoding:          lattice      n-best         n-best/beam
decoding beam:     13.0         13.0           13.0  
lattice beam:      9.2          --             9.35 [6.0-12.5] (few outliers below/above)
N best:            --           <=20           206.96 [2-1600] (according to beam range and utterance)
max tokens:        15000        150k,700k      150000-770000
avg. link density: 13.58        14?            231.05
realtime factor:   1.77         12             crap

decoding WER:      10.80%       12.78% (why?)  14.96% (probably too low max tokens)
ins/del/sub:       120/47/442
utterances wrong:  215

oracle WER:        3.19%
ins/del/sub:       33/1/146
oracle utt wrong:  107

rescoring WER(15):  9.87%
ins/del/sub:       119/38/400
rescore utt wrong: 209
